---
title: "DATA 698 - Capstone"
author: "Sreejava, Suman, Vuthy"
date: "March 22, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
In an effort to reduce traffic fatalities and injuries, NYC released the Vision Zero Action Plan in 2014. The Vision Zero action plan included many initiatives but one of the more known initiative was reducing the citywide speed limit from 30 mph to 25 mph. How effective was reduction of the speed limit at lowering injuries and fatalities? Does reducing the speed limit actually decrease the number of motor vehicle accidents and/or traffic violations? As more traffic violations can lead to increased accidents, can we identify traffic black spots (areas with recurring traffic violations)? In this study, we would plan on applying data mining algorithms like K-means and SVD to identify clusters in the data and build forecasting models to forecast the future traffic violations at specific locations.  

**Dataset**  
[NYC Traffic Tickets](https://github.com/psumank/DATA698/raw/master/Data/Traffic_Tickets_Issued__NYC.zip)  
[NYC Motor Vehicle Collision](https://github.com/psumank/DATA698/raw/master/Data/NYPD_Motor_Vehicle_Collisions.zip)  
[Vision Zero](http://www.nyc.gov/html/dot/html/about/vz_datafeeds.shtml)  

```{r read data, eval=FALSE}
nyc.collision.csv  <- read.csv("Data/NYPD_Motor_Vehicle_Collisions.csv",
                               header=TRUE, sep=",", stringsAsFactors = FALSE,
                               na.strings=c("NA", ""))
nyc.trafficViolations.csv  <- read.csv("Data/Traffic_Tickets_Issued__NYC.csv",
                                       header=TRUE, sep=",", stringsAsFactors = 
                                         FALSE, na.strings=c("NA", ""))

df.coll <- data.frame(nyc.collision.csv)

pedestrian <- df.coll[(df.coll$NUMBER.OF.CYCLIST.INJURED > 0) 
                      | (df.coll$NUMBER.OF.CYCLIST.KILLED > 0) 
                      | (df.coll$NUMBER.OF.PEDESTRIANS.INJURED > 0) 
                      | (df.coll$NUMBER.OF.PEDESTRIANS.KILLED > 0) ,]

write.csv(pedestrian, file = "Data/pedestrian.csv")

```

```{r}
peds <- read.csv("Data/pedestrian.csv")

```

Possible Tutorials

Lat/Lon falls within GeoJson
https://github.com/rgeo/rgeo-geojson/issues/11

https://blog.exploratory.io/creating-geojson-out-of-shapefile-in-r-40bc0005857d
https://andrewbtran.github.io/NICAR/2017/maps/mapping-census-data.html


## Data Exploration

## Data Preparation

## Model Selection

## Evaluation

## Conclusion
